Information Closure Theory of Consciousness

### 2019-09-28 Paper_neural_coarse_graining_of_consciousness.tex
First submission
Updates from Overleaf

% ============================================================================ %
%                                     Body                                     %
% ============================================================================ %
\begin{document}
    \linenumbers
	\maketitle
	\tableofcontents

@@

    	    According to Sec.~\ref{sec:cl} and Sec.~\ref{sec:cc}, an important implication from \ac{OurTheory} is that both conscious levels and conscious contents are associated with the state space of an NTIC process $Y$. A large state space of $Y$ contributes conscious levels through the mutual information $I(Y_{t+1};Y_{t})$ and also contributes richer conscious contents by providing more possbile states of conscious processes. 
    	    \ac{OurTheory} therefore explains why, in normal physiological states, conscious levels and conscious contents are often positively correlated \citep{laureys2005neural}. This implication is also in line with the intuition in which consciousness is often associated with complex systems.

@@

             	% reflexive behaviour
        		\begin{figure}[H]
        			\includegraphics[width=0.8\textwidth]{WritingMaterials/Fig_Reflexive/Reflexive.pdf}
        			\caption{
        			    A diagram depicting the information flow in reflexive behaviours (shown by the red nodes and arrows) happening through the interaction between a process $Y$ and its environment $E$. In such situations, the internal state $Y_t$ is mostly dependent on the environment state $E_{t-1}$ but less on its past state $Y_{t-1}$. Therefore, the process $Y$ is not informational closed. As a  consequence, $Y$ is unable to form high NTIC and, therefore, remain lesss conscious or unconscious. 
        			    }
        			\label{fig:reflexive}
        		\end{figure}

@@

	% For philosophy of mind
	Regarding philosophy of mind, \ac{OurTheory} connects several distinct arguments together. \ac{OurTheory} can be seen as an identity theory because it assumes a fundamental relation between consciousness and information. Second, the implications of \ac{OurTheory} tightly link consciousness to several cognitive functions in the context of evolution. This explains why people might intuitively have a functionalist point of view of consciousness. \ac{OurTheory} emphasises that informational closure between levels of coarse-graining is critical to form NTIC processes in some stochastic systems. In this case, especially for the neural system, forming conscious processes at the macroscopic levels coincide with the perspective of emergentism. Finally, forming NTIC (conscious) processes through many-to-one maps, i.e., coarse-graining, implies multiple realizability of consciousness. As a result, \ac{OurTheory} provides an integrated view for these arguments and is further capable of indicating how and why they are conditionally true.
W
	% Final 
	So far, the current version of \ac{OurTheory} is still far from completion. Further theoretical and empirical research is indispensably required for \ac{OurTheory} to improve and solve several issues in the current version. Nevertheless, \ac{OurTheory} offers explanation and prediction for consciousness science. We hope that \ac{OurTheory} provides a new way of thinking and understanding neural substrates of consciousness.

>>>>

% ============================================================================ %
%                                     Body                                     %
% ============================================================================ %
\begin{document}
    % \linenumbers
	\maketitle
	\tableofcontents

@@

    	    According to Sec.~\ref{sec:cl} and Sec.~\ref{sec:cc}, an important implication from \ac{OurTheory} is that both conscious levels and conscious contents are associated with the state space of an NTIC process $Y$. A large state space of $Y$ contributes conscious levels through the mutual information $I(Y_{t+1};Y_{t})$ and also contributes richer conscious contents by providing more possible states of conscious processes. 
    	    \ac{OurTheory} therefore explains why, in normal physiological states, conscious levels and conscious contents are often positively correlated \citep{laureys2005neural}. This implication is also in line with the intuition in which consciousness is often associated with complex systems.

@@

             	% reflexive behaviour
        		\begin{figure}[H]
        			\includegraphics[width=0.8\textwidth]{WritingMaterials/Fig_Reflexive/Reflexive.pdf}
        			\caption{
        			    A diagram depicting the information flow in reflexive behaviours (shown by the red nodes and arrows) happening through the interaction between a process $Y$ and its environment $E$. In such situations, the internal state $Y_t$ is mostly dependent on the environment state $E_{t-1}$ but less on its past state $Y_{t-1}$. Therefore, the process $Y$ is not informational closed. As a  consequence, $Y$ is unable to form high NTIC and, therefore, remain less conscious or unconscious. 
        			    }
        			\label{fig:reflexive}
        		\end{figure}

@@

	% For philosophy of mind
	Regarding philosophy of mind, \ac{OurTheory} connects several distinct arguments together. \ac{OurTheory} can be seen as an identity theory because it assumes a fundamental relation between consciousness and information. Second, the implications of \ac{OurTheory} tightly link consciousness to several cognitive functions in the context of evolution. This explains why people might intuitively have a functionalist point of view of consciousness. \ac{OurTheory} emphasises that informational closure between levels of coarse-graining is critical to form NTIC processes in some stochastic systems. In this case, especially for the neural system, forming conscious processes at the macroscopic levels coincide with the perspective of emergentism. Finally, forming NTIC (conscious) processes through many-to-one maps, i.e., coarse-graining, implies multiple realisability of consciousness. As a result, \ac{OurTheory} provides an integrated view for these arguments and is further capable of indicating how and why they are conditionally true.

	% Final 
	So far, the current version of \ac{OurTheory} is still far from completion. Further theoretical and empirical research is indispensably required for \ac{OurTheory} to improve and solve several issues in the current version. Nevertheless, \ac{OurTheory} offers explanation and prediction for consciousness science. We hope that \ac{OurTheory} provides a new way of thinking and understanding neural substrates of consciousness.
